Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-01-28 hscc2017/paper.tex
copyright
wording

%
In Figure~\ref{fig:digsystem1}, two sources of uncertainty are illustrated:
parametric uncertainties related to modeling errors, and uncertainties
introduced by quantizations in sampling and holding process, i.e., ADC and
DAC conversions.  Assuming linearity and independence between these sources,
the uncertain model may be rewritten as a vector of coefficients in the
z-domain using equations (\ref{eq:coefficients}) and
(\ref{eq:delta_coefficients})
%
\begin{equation}
\label{eq:complete_unc_model}
\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G},
\end{equation}
%
where $\Delta_p \vec{G}$ is the term that corresponds to the parametric
uncertainties and $\Delta_q \vec{G}$ is the term that reflects the
quantization effects on the plant model, {\it i.e.} $\Delta_q \vec{G}$ is 
a model that incorporates the effects of $\nu$ in $\vec{\hat{G}}$ to 
investigate the consequences in the stability of system, once our stability 
analysis is based on polynomial coefficients and not over signals.

>>>>

%
In Figure~\ref{fig:digsystem1}, two sources of uncertainty are illustrated:
parametric uncertainties related to modeling errors, and uncertainties
introduced by quantizations in sampling and holding process, i.e., ADC and
DAC conversions.  These sources are assumed to be non-deterministic, 
which poses no further restriction to our model, thus, the uncertain model
may be rewritten as a vector of coefficients in the z-domain using equations
(\ref{eq:coefficients}) and (\ref{eq:delta_coefficients})
%
\begin{equation}
\label{eq:complete_unc_model}
\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G},
\end{equation}
%
where $\Delta_p \vec{G}$ is the term that corresponds to the parametric
uncertainties and $\Delta_q \vec{G}$ is the term that reflects the
quantization effects on the plant model, {\it i.e.} $\Delta_q \vec{G}$ is 
a model that incorporates the effects of $\nu$ in $\vec{\hat{G}}$ to 
investigate the consequences in the stability of system, once our stability 
analysis is based on polynomial coefficients and not over signals.

The parametric uncertainties in the plant are assumed to have the same
order as the plant model, since tolerances of higher order would invalidate
feedback model (even tiny errors of higher order can move the poles by a
large amount preventing any single controller from stabilizing such a setup).
This is a reasonable assumption since most tolerances do not change the 
architecture of the plant, and models subject to such effects are
inadequate.
